---
title: "Use CORE API in R"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The **CORE API** appears to be for accessing data related to public procurement in Italy. Specifically, it provides access to information on suppliers ( _Aggiudicatari_), offered contracts ( _Cigs_), and public contracting stations ( _Stazione Appaltante_).
Many others endpoints (pointing to each of the resources in our database) including indicators are going to be provided soon.

To use the API, you will need to provide an **API key** in the header of your requests (if you are willing to try it just reach out to the [maintainer](mailto:niccolo.salvini27@gmail.com) providing monthly usage and purpose). The possible parameters for each endpoint are listed in the Swagger API specs, and may include information such as a limit on the number of results returned, filtering by *codice_fiscale*, *denominazione*, *provincia*, and other factors depending on the endpoint.

You can call the API using the R functions provided in the following response, or using another programming language or toolset that can handle RESTful APIs. Depending on your needs, you can also use the JSON response data to create reports, analyze trends, or visualize data related to public procurement in Italy.


```{r api, eval=FALSE}
library(httr)

# Set the API endpoint for the Dev environment
url <- "https://g7x6h7tfvk.execute-api.eu-west-2.amazonaws.com/dev"

# Create a function to call the /aggiudicatari endpoint
get_aggiudicatari <- function(api_key, limit, cig = NULL, ruolo = NULL, codice_fiscale = NULL,
                              denominazione = NULL, tipo_soggetto = NULL, id_aggiudicazione = NULL,
                              sort_param = NULL) {
  # Set the API endpoint for the /aggiudicatari endpoint
  endpoint <- "/aggiudicatari"

  # Create the request URL with the specified parameters
  request_url <- paste0(url, endpoint, "?limit=", limit)
  if (!is.null(cig)) request_url <- paste0(request_url, "&cig=", cig)
  if (!is.null(ruolo)) request_url <- paste0(request_url, "&ruolo=", ruolo)
  if (!is.null(codice_fiscale)) request_url <- paste0(request_url, "&codice_fiscale=", codice_fiscale)
  if (!is.null(denominazione)) request_url <- paste0(request_url, "&denominazione=", denominazione)
  if (!is.null(tipo_soggetto)) request_url <- paste0(request_url, "&tipo_soggetto=", tipo_soggetto)
  if (!is.null(id_aggiudicazione)) request_url <- paste0(request_url, "&id_aggiudicazione=", id_aggiudicazione)
  if (!is.null(sort_param)) request_url <- paste0(request_url, "&sort_param=", sort_param)

  # Make the API request with the API key in the header
  response <- GET(request_url, add_headers("x-api-key" = api_key))

  # Return the response as a JSON object
  content(response, as = "parsed")
}

# Create a function to call the /cigs endpoint
get_cigs <- function(api_key, limit, cig = NULL, provincia = NULL, tipo_scelta_contraente = NULL,
                     data_pubblicazione_min = NULL, data_pubblicazione_max = NULL,
                     importo_lotto_min = NULL, importo_lotto_max = NULL) {
  # Set the API endpoint for the /cigs endpoint
  endpoint <- "/cigs"

  # Create the request URL with the specified parameters
  request_url <- paste0(url, endpoint, "?limit=", limit)
  if (!is.null(cig)) request_url <- paste0(request_url, "&cig=", cig)
  if (!is.null(provincia)) request_url <- paste0(request_url, "&provincia=", provincia)
  if (!is.null(tipo_scelta_contraente)) request_url <- paste0(request_url, "&tipo_scelta_contraente=", tipo_scelta_contraente)
  if (!is.null(data_pubblicazione_min)) request_url <- paste0(request_url, "&data_pubblicazione_min=", data_pubblicazione_min)
  if (!is.null(data_pubblicazione_max)) request_url <- paste0(request_url, "&data_pubblicazione_max=", data_pubblicazione_max)
  if (!is.null(importo_lotto_min)) request_url <- paste0(request_url, "&importo_lotto_min=", importo_lotto_min)
  if (!is.null(importo_lotto_max)) request_url <- paste0(request_url, "&importo_lotto_max=", importo_lotto_max)

  # Make the API request with the API key in the header
  response <- GET(request_url, add_headers("x-api-key" = api_key))

  # Return the response as a JSON object
  content(response, as = "parsed")
}

# Create a function to call the /stazione-appaltante endpoint
get_stazione_appaltante <- function(api_key, limit, codice_fiscale = NULL, partita_iva = NULL,
                                    denominazione = NULL, provincia_nome = NULL, citta_codice = NULL,
                                    citta_nome = NULL, sort_param = NULL) {
  # Set the API endpoint for the /stazione-appaltante endpoint
  endpoint <- "/stazione-appaltante"

  # Create the request URL with the specified parameters
  request_url <- paste0(url, endpoint, "?limit=", limit)
  if (!is.null(codice_fiscale)) request_url <- paste0(request_url, "&codice_fiscale=", codice_fiscale)
  if (!is.null(partita_iva)) request_url <- paste0(request_url, "&partita_iva=", partita_iva)
  if (!is.null(denominazione)) request_url <- paste0(request_url, "&denominazione=", denominazione)
  if (!is.null(provincia_nome)) request_url <- paste0(request_url, "&provincia_nome=", provincia_nome)
  if (!is.null(citta_codice)) request_url <- paste0(request_url, "&citta_codice=", citta_codice)
  if (!is.null(citta_nome)) request_url <- paste0(request_url, "&citta_nome=", citta_nome)
  if (!is.null(sort_param)) request_url <- paste0(request_url, "&sort_param=", sort_param)

  # Make the API request with the API key in the header
  response <- GET(request_url, add_headers("x-api-key" = api_key))

  # Return the response as a JSON object
  content(response, as = "parsed")
}
```


To use any of these functions, simply provide the required inputs (such as the api_key and limit parameters) along with any optional parameters (such as cig or provincia) according to the Swagger API specifications. For example:


```{r apiUsageExamples, eval=FALSE}
# free usage plan (limited to Rate 100 requests per second, Burst 100 requests,Quota 10,000 requests per month starting on the 1st day)
free_usage_api_key <- "m4JqlGtSl8aZyAIRyPzd3mPTFCO7VC2vo9O7Xpc0"

# Call the /aggiudicatari endpoint with a limit of 10 and a codice_fiscale of "6960001684"
get_aggiudicatari(api_key = free_usage_api_key, limit = 10)

# Call the /cigs endpoint with a limit of 20 and a minimum lotto import of 1000000
get_cigs(api_key = free_usage_api_key, limit = 20, importo_lotto_min = 1000000)

# Call the /stazione-appaltante endpoint with a limit of 5 and a province name of "MILANO"
get_stazione_appaltante(api_key = free_usage_api_key, limit = 5, provincia_nome = "MILANO")
```
